Evolutionary Design of Particles for Collectively Intelligent Problem Solving

### 2014-05-08 docs/paper.tex
moving to editing mode

\[ \vec { v_{ c } } =v_{ max }\frac { \Delta  \vec { p }  }{ \left\|   \Delta \vec { p }  \right\|  } \left( \frac { \left\|  \Delta \vec {  p }  \right\|  }{ r }  \right) ^{ 2 } \]

@@

\[ \vec { v_{ al } } =v_{ max }{\left( \frac { \left\| \Delta \vec { p } \right\|  }{ r }  \right)}^2\frac {\Delta \vec{v}} { \left\| \Delta \vec{v} \right\| } \]

@@

\[ \vec { v_{ d } } =-v_{ max }\frac {\Delta \vec{p}} { \left\| \Delta \vec{p} \right\| }{\left( \frac { r - \left\| \Delta \vec { p } \right\|  }{ r }  \right)}^2 \]

@@

\[ \vec{v_h} = v_{max} \frac {\vec{p_t} - \vec p} { \left\| \vec{p_t} - \vec p \right\| } \]

@@

\[ \vec{v_{cl}} = v_{max} \frac {\Delta \vec p_\perp } { \left\| \Delta \vec p_\perp  \right\| }  \]

@@

\[ \vec { v_{ av } } =\sum _{i=0}^{n} {v_{ max } \left( \frac{r - \left\| \Delta \vec{p_e} \right\|} {r} \right) \frac { \Delta \vec { p_e }  }{ \left\| \Delta \vec { p_e }  \right\|  }}  \]

@@

The recombination operator ... %TODO talk about recombination

@@

\begin{figure}[h!]
    \centering
        \includegraphics[width=0.5\textwidth]{figures/head2head}
    \caption{Performance of evolved particles vs human designed particles in head to head simulation of 10,000 timesteps}
    \label{fig:head2head}
\end{figure}

@@

\begin{figure}[h!]
    \centering
        \includegraphics[width=0.5\textwidth]{figures/meanfit_experiment1}
    \caption{Mean fitness per generation with mutation}
    \label{fig:meanfit1}
\end{figure}

\begin{figure}[h!]
    \centering
        \includegraphics[width=0.5\textwidth]{figures/fitness21}
    \caption{Mean fitness per generation with mutation and recombination}
    \label{fig:meanfit2}
\end{figure}

>>>>

\begin{equation}
    \vec { v_{ c } } =v_{ max }\frac { \Delta  \vec { p }  }{ \left\|   \Delta \vec { p }  \right\|  } \left( \frac { \left\|  \Delta \vec {  p }  \right\|  }{ r }  \right) ^{ 2 }
    \label{eqn:cohesion}
\end{equation}

@@

\begin{equation}
    \vec { v_{ al } } =v_{ max }{\left( \frac { \left\| \Delta \vec { p } \right\|  }{ r }  \right)}^2\frac {\Delta \vec{v}} { \left\| \Delta \vec{v} \right\| }
    \label{eqn:alignment}
\end{equation}

@@

\begin{equation}
    \vec { v_{ d } } =-v_{ max }\frac {\Delta \vec{p}} { \left\| \Delta \vec{p} \right\| }{\left( \frac { r - \left\| \Delta \vec { p } \right\|  }{ r }  \right)}^2
    \label{eqn:separation}
\end{equation}

@@

\begin{equation}
    \vec{v_h} = v_{max} \frac {\vec{p_t} - \vec p} { \left\| \vec{p_t} - \vec p \right\| }
    \label{eqn:seeking}
\end{equation}

@@

\begin{equation}
    \vec{v_{cl}} = v_{max} \frac {\Delta \vec p_\perp } { \left\| \Delta \vec p_\perp  \right\| }
    \label{eqn:clearance}
\end{equation}

@@

\begin{equation}
    \vec { v_{ av } } =\sum _{i=0}^{n} {v_{ max } \left( \frac{r - \left\| \Delta \vec{p_e} \right\|} {r} \right) \frac { \Delta \vec { p_e }  }{ \left\| \Delta \vec { p_e }  \right\|  }}
    \label{eqn:avoidance}
\end{equation}

@@

The recombination operator also ignored the elite individuals carried over from the last population. Parents were selected with a likelihood of 0.2 to be recombined with another individual. Our recombination operator replaced the first parent with intermediary recombination, that is the mean value of the parents velocity parameters. The second chosen parent remained in the population. Although elite individuals were exempt from recombination, they were able to be selected as the secondary parent, contributing their genetic material to the recombined offspring.

@@

\begin{figure}[ht!]
    \centering
        \includegraphics[width=0.5\textwidth]{figures/head2head}
    \caption{Performance of evolved particles vs human designed particles in head to head simulation of 10,000 timesteps}
    \label{fig:head2head}
\end{figure}

@@

\begin{figure}[ht!]
    \centering
        \includegraphics[width=0.5\textwidth]{figures/meanfit_experiment1}
    \caption{Mean fitness per generation with mutation}
    \label{fig:meanfit1}
\end{figure}

\begin{figure}[ht!]
    \centering
        \includegraphics[width=0.5\textwidth]{figures/fitness46}
    \caption{Mean fitness per generation with mutation and recombination}
    \label{fig:meanfit2}
\end{figure}
